### 2010-09-14 proposal/preProposal.tex
Schedule done, skeleton less skeletony :).

1.The Team. Names of the people working on the project. We suggest
working in groups of about three, but can be convinced otherwise if
you have a good reason. If you can’t find a group, email the TAs and
we will assign you to a group.

@@

@@

9.Schedule. A schedule of work indicating the dates by which you plan
to complete components of the system. This should be presented as a
table listing dates and milestones.

>>>>

The human members of our team are Diana Hidalgo, Sarah Nguyen, and
Jason Yosinski.  The sole robotic member of our team is a 9 DoF
starfish shaped robot from Hod Lipson's lab.

@@

\edit{todo}

@@

Below is a rough schedule of fixed external deadlines and anticipated
team milestones.

\begin{center}
\begin{tabular}{|l||p{2.5in}|p{1.5in}|}
\hline
                        & {\bf Milestones} & {\bf Deadlines}
\\ \hline

Week 1 (9/13-9/19)    & Read papers, get lab access, talk to relevant other researchers & 9/17 Final proposals due
\\ \hline

Week 2 (9/20-9/26)    & Continue reading, get robot to move &
\\ \hline

Week 3 (9/27-10/03)   & Implement parametrized gait and determine proposed coding schedule for more advanced algorithms in time for Code Review \#1. &
\\ \hline

Week 4 (10/04-10/10)  & Begin main algorithm dev/testing effort & 10/5 Code Review \#1
\\ \hline

Week 5 (10/11-10/17)  & Algorithm dev/testing &
\\ \hline

Week 6 (10/18-10/24)  & Algorithm dev/testing &
\\ \hline

Week 7 (10/25-10/31)  & Algorithm dev/testing, quantify/solidify current results for Code Review \#2 &
\\ \hline

Week 8 (11/1-11/7)    & Finish collecting results, begin writing & 11/2 Code RReview \#2
\\ \hline

Week 9 (11/8-11/14)   & Finish collecting results, writing &
\\ \hline

Week 10 (11/15-11/21) & Finish collecting results, writing, get final demo ready &
\\ \hline

Week 11 (11/22-11/28) & Finish collecting results, writing, get final demo ready  &
\\ \hline

Week 12 (11/29-11/30) & Final demo  & 11/30 Final presentation
\\ \hline
\end{tabular}
\end{center}
